---
title: "Data analysis"
author: "Sofia F. M. Schmidt-Kallesøe"
date: "19/11/2018"
output: html_document
---


```{r}

dataframe = read.csv("cleanData.csv")
library(stats)
library(ggplot2)
library(psych)
library(knitr)
library(xtable)

```


Average of main traits separated by condition  
```{r}

round(by(dataframe$achievement_orientation, dataframe$cond, FUN = mean), 2)
round(by(dataframe$autonomy, dataframe$cond, FUN = mean()), 2)
round(by(dataframe$take_charge, dataframe$cond, FUN = mean), 2)
round(by(dataframe$rational, dataframe$cond, FUN = mean), 2)

round(by(dataframe$affiliative, dataframe$cond, FUN = mean), 2)
round(by(dataframe$deference, dataframe$cond, FUN = mean), 2)
round(by(dataframe$emotionally_sensitive, dataframe$cond, FUN = mean), 2)
round(by(dataframe$concern_for_others, dataframe$cond, FUN = mean), 2)

by(dataframe$law_dk, dataframe$cond, summary)

plot(density(dataframe$male_stereotype))
plot(density(dataframe$female_stereotype))

```

Checking reliability with Alpha package for each main trait for all data
```{r}

achievement_orientation = subset(dataframe, select = c(competence, ambition, project))
alpha(achievement_orientation)

deference = subset(dataframe, select = c(obedient, respectful, self_erase))
alpha(deference)

autonomy = subset(dataframe, select = c(independent, self_reliant, decisive))
alpha(autonomy)

affiliative = subset(dataframe, select = c(warm, friendly, cooperative))
alpha(affiliative)

emotionally_sensitive = subset(dataframe, select = c(sharp, intuitive, insightful))
alpha(emotionally_sensitive)

take_charge = subset(dataframe, select = c(confident, dominant, forceful))
alpha(take_charge)

rational = subset(dataframe, select = c(analytic, logical, objective))
alpha(rational)

concern_for_others = subset(dataframe, select = c(friendly2, caring, considerate))
alpha(concern_for_others)

```


Main trait correlations 
```{r}

main_trait_correlations = psych::corr.test(dataframe[45:52])
main_trait_correlations_df = as.data.frame(main_trait_correlations$r) #extracting correlations from the corr.test

kable(main_trait_correlations_df, digits = 2, align = "c", format = "pandoc", caption = "Main Trait Correlations")

```


-------------------------------------------------------------------------------------------------------------------------------



Vote as outcome
```{r}

votemodel1 = lm(vote ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(votemodel1)

votemodel2 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(votemodel2)


by(dataframe$male_stereotype, dataframe$cond, FUN = mean)
by(dataframe$female_stereotype, dataframe$cond, FUN = mean)

by(subset(dataframe, gender == "Male")$vote, subset(dataframe, gender == "Male")$cond, FUN = mean)
by(subset(dataframe, gender == "Female")$female_stereotype, subset(dataframe, gender == "Female")$cond, FUN = mean)

```

Plotting significant interaction between genderMale:female_stereotype with vote as outcome in experiment 1
```{r}

 ggplot(subset(dataframe, experiment == "1"), aes(female_stereotype, vote, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Female Stereotype", y = "Vote")

 ggplot(subset(dataframe, experiment == "1"), aes(female_stereotype, vote, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Female Stereotype", y = "Vote")

```


Plotting significant interaction between condStandardMale:genderMale:female_stereotype with vote as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(female_stereotype, vote, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond) +
  labs(x = "Female Stereotype", y = "Vote")
  
```



Representation (me)
-------------------------------------------------------------------------------------------------------------------------------
Representation (me) within foreign policy as outcome
```{r}

me_foreign1 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_foreign1)

me_foreign2 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_foreign2)

```

Representation (me) within education policy as outcome
```{r}

me_education1 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_education1)

me_education2 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_education2)

```

Representation (me) within health policy as outcome
```{r}

me_health1 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_health1)

me_health2 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_health2)

```

Representation (me) within law policy as outcome
```{r}

me_law1 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_law1)

me_law2 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_law2)

```
-------------------------------------------------------------------------------------------------------------------------------


Representation (dk)
-------------------------------------------------------------------------------------------------------------------------------

Representation (dk) within foreign policy as outcome
```{r}

dk_foreign1 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_foreign1)

dk_foreign2 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_foreign2)

```


Plotting significant interaction between genderMale:male_stereotype with foreign_dk as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(male_stereotype, foreign_dk, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Male Stereotype", y = "Representation of Denmark in foreign law")

```

Plotting significant interaction between condStandardMale:genderMale:male_stereotype with foreign_dk as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(male_stereotype, foreign_dk, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond) +
  labs(x = "Male Stereotype", y = "Representation of Denmark in foreign law")

```




Representation (dk) within education policy as outcome
```{r}

dk_education1 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_education1)

dk_education2 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_education2)

```


Plotting significant interaction between condWarmFemale:female_stereotype with foreign_dk as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, education_dk, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3)

```




Representation (dk) within health policy as outcome
```{r}

dk_health1 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_health1)

dk_health2 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_health2)

```

Representation (dk) within law policy as outcome
```{r}

dk_law1 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_law1)

dk_law2 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_law2)

```


Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with law_dk as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, law_dk, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond)

```


-------------------------------------------------------------------------------------------------------------------------------

Sociability
-------------------------------------------------------------------------------------------------------------------------------

Sociability as outcome
```{r}

socmodel1 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(socmodel1)

socmodel2 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(socmodel2)

```
-------------------------------------------------------------------------------------------------------------------------------

Trustworthiness
-------------------------------------------------------------------------------------------------------------------------------

Trustworthiness as outcome
```{r}

trustmodel1 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(trustmodel1)

trustmodel2 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(trustmodel2)

```


Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with trustworthiness as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, trustworthy, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond)

```



-------------------------------------------------------------------------------------------------------------------------------

Suitability
-------------------------------------------------------------------------------------------------------------------------------

Suitability as outcome
```{r}

suitmodel1 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(suitmodel1)

suitmodel2 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(suitmodel2)

```

Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with suitability as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, gender_suitability, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond)

```

-------------------------------------------------------------------------------------------------------------------------------







```{r}

library(ggplot2)


ggplot(dataframe, aes(female_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


ggplot(dataframe, aes(male_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


```

PLOTS
```{r}

library(ggplot2)

#Histograms of stereotypes
plot(hist(dataframe$male_stereotype))
plot(hist(dataframe$female_stereotype))



ggplot(dataframe, aes(female_stereotype, vote)) + 
  geom_point() + 
  geom_smooth(method = "lm")

ggplot(dataframe, aes(male_stereotype, vote)) + 
  geom_point() + 
  geom_smooth(method = "lm")

ggplot(dataframe, aes(female_stereotype, vote, colour = gender)) +
  stat_summary(fun.y = mean, geom = "point") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = gender)) + 
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  facet_wrap(~cond)
#remember stereotypes 


plot(dataframe$female_stereotype[dataframe$experiment==2 & dataframe$gender=="Kvinde" & dataframe$cond=="Warm female candidate"],
     dataframe$suitability[dataframe$experiment==2 & dataframe$gender=="Kvinde" & dataframe$cond=="Warm female candidate"])


ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, gender_suitability)) + 
  facet_wrap(cond~gender) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Female Stereotype", y = "Gender Suitability")








```



```{r}

count(subset(dataframe1, experiment == "2")$gender == "Female")

plot(subset(dataframe, experiment == "2")$age)


```