---
title: "Data cleanup"
author: "Sofia F. M. Schmidt-Kallesøe"
date: "9/10/2018"
output: html_document
---

Josh's cleanup
```{r}

library(foreign) #read.spss function

# read SPSS data file
dat_in = read.spss("/Users/Fred/Documents/Aarhus/5. Semester/Bachelor/Gender in politics data/DK2017_Lea.sav")

#######################################################
####------Parsing SPSS file into responses to each question

#----------Question 1 ---------------------
# judgements of candidate in vignette
# check with Lea to verify titles
cond <- dat_in$basic_design
competence <-as.numeric(substr(dat_in$Q1_1,1,1))
ambition <-as.numeric(substr(dat_in$Q1_2,1,1))
project <-as.numeric(substr(dat_in$Q1_3,1,1))
obedient <-as.numeric(substr(dat_in$Q1_4,1,1))
respectful<-as.numeric(substr(dat_in$Q1_5,1,1))
self_erase<-as.numeric(substr(dat_in$Q1_6,1,1))
independent<-as.numeric(substr(dat_in$Q1_7,1,1))
self_reliant<-as.numeric(substr(dat_in$Q1_8,1,1))
decisive<-as.numeric(substr(dat_in$Q1_9,1,1))
warm<-as.numeric(substr(dat_in$Q1_10,1,1))
friendly<-as.numeric(substr(dat_in$Q1_11,1,1))
cooperative<-as.numeric(substr(dat_in$Q1_12,1,1))
sharp<-as.numeric(substr(dat_in$Q1_13,1,1))
intuitive<-as.numeric(substr(dat_in$Q1_14,1,1))
insightful<-as.numeric(substr(dat_in$Q1_15,1,1))
confident<-as.numeric(substr(dat_in$Q1_16,1,1))
dominant<-as.numeric(substr(dat_in$Q1_17,1,1))
forceful<-as.numeric(substr(dat_in$Q1_18,1,1))
analytic<-as.numeric(substr(dat_in$Q1_19,1,1))
logical<-as.numeric(substr(dat_in$Q1_20,1,1))
objective<-as.numeric(substr(dat_in$Q1_21,1,1))
friendly2<-as.numeric(substr(dat_in$Q1_22,1,1))
caring<-as.numeric(substr(dat_in$Q1_23,1,1))
considerate<-as.numeric(substr(dat_in$Q1_24,1,1))

#------Question 2 and 3 ---------------------------
# representation
foreign_me <- as.numeric(substr(dat_in$Q2_1,1,1))
education_me <- as.numeric(substr(dat_in$Q2_2,1,1))
health_me <- as.numeric(substr(dat_in$Q2_3,1,1))
law_me <- as.numeric(substr(dat_in$Q2_4,1,1))

foreign_dk <- as.numeric(substr(dat_in$Q3_1,1,1))
education_dk <- as.numeric(substr(dat_in$Q3_2,1,1))
health_dk <- as.numeric(substr(dat_in$Q3_3,1,1))
law_dk <- as.numeric(substr(dat_in$Q3_4,1,1))

#------Question 4 ---------------------------
# judgements of sociability and trustworthyness
sociability <- rowSums(cbind(as.numeric(substr(dat_in$Q4a_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4b_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4c_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4d_socialibility,1,1))))

trustworthy <- rowSums(cbind(as.numeric(substr(dat_in$Q4e_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4f_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4g_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4h_moral_trustworthy,1,1))))

#------Question 5, 6, and 7 ---------------------------
# voting, suitability, and ability to explicitly recall target gender
vote <- as.numeric(substr(dat_in$Q5,1,1))
gender_suitability <- as.numeric(substr(dat_in$Q6,1,1))
gender_recall <- dat_in$Q7

gender_correct <- rep(1,length(gender_recall))
gender_correct[cond=="Standard female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Warm female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Competent female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Standard male candidate"&gender_recall == "Kvinde"]=0
gender_correct[gender_recall == "Ved ikke"]=0

#------ participant demographics and experiment/condition information
gender <- dat_in$gender

experiment <- rep(1,length(competence))
experiment[cond=="Warm female candidate"|cond=="Competent female candidate"] <- 2

sub <- dat_in$RecordNo


```

Creating one big dataframe with all the data
```{r}

participant = list(1:1006) #list of numbers 1-1006

dataframe = data.frame(participant, cond, 
                       
                       competence, ambition, project, 
                       independent, self_reliant, decisive, 
                       analytic, logical, objective,
                       confident, dominant, forceful,
                       obedient, respectful, self_erase,  
                       warm, friendly, cooperative, 
                       sharp, intuitive, insightful,  
                       friendly2, caring, considerate, 
                       
                       foreign_me, education_me, health_me, law_me,
                       foreign_dk, education_dk, health_dk, law_dk,
                       
                       sociability, trustworthy,
                       
                       vote, gender_suitability, gender_recall, gender_correct, gender)

dataframe = plyr::rename(dataframe, c("X1.1006" = "participant")) #renaming participant column

```


Removing data from people who didn't recall gender correctly 
```{r}

dataframe = dataframe[!(dataframe$gender_correct == "0"),]

```


Adding main traits in the dataframe 
```{r}

dataframe$achievement_orientation = (dataframe$competence + dataframe$ambition + dataframe$project)/3
dataframe$deference = (dataframe$obedient + dataframe$respectful + dataframe$self_erase)/3
dataframe$autonomy = (dataframe$independent + dataframe$self_reliant + dataframe$decisive)/3
dataframe$affiliative = (dataframe$warm + dataframe$friendly + dataframe$cooperative)/3
dataframe$emotionally_sensitive = (dataframe$sharp + dataframe$intuitive + dataframe$insightful)/3
dataframe$take_charge = (dataframe$confident + dataframe$dominant + dataframe$forceful)/3
dataframe$rational = (dataframe$analytic + dataframe$logical + dataframe$objective)/3
dataframe$concern_for_others = (dataframe$friendly2 + dataframe$caring + dataframe$considerate)/3

```

Average of main traits separated by condition  
```{r}

by(dataframe$achievement_orientation, dataframe$cond, FUN = mean)
by(dataframe$deference, dataframe$cond, FUN = mean)
by(dataframe$autonomy, dataframe$cond, FUN = mean)
by(dataframe$affiliative, dataframe$cond, FUN = mean)
by(dataframe$emotionally_sensitive, dataframe$cond, FUN = mean)
by(dataframe$take_charge, dataframe$cond, FUN = mean)
by(dataframe$rational, dataframe$cond, FUN = mean)
by(dataframe$concern_for_others, dataframe$cond, FUN = mean)

```


Checking reliability with Alpha package for each main trait for all data
```{r}

library(psych)

achievement_orientation = subset(dataframe, select = c(competence, ambition, project))
alpha(achievement_orientation)

deference = subset(dataframe, select = c(obedient, respectful, self_erase))
alpha(deference)

autonomy = subset(dataframe, select = c(independent, self_reliant, decisive))
alpha(autonomy)

affiliative = subset(dataframe, select = c(warm, friendly, cooperative))
alpha(affiliative)

emotionally_sensitive = subset(dataframe, select = c(sharp, intuitive, insightful))
alpha(emotionally_sensitive)

take_charge = subset(dataframe, select = c(confident, dominant, forceful))
alpha(take_charge)

rational = subset(dataframe, select = c(analytic, logical, objective))
alpha(rational)

concern_for_others = subset(dataframe, select = c(friendly2, caring, considerate))
alpha(concern_for_others)

```


Main trait correlations 
```{r}

library(knitr)
library(xtable)

main_trait_correlations = psych::corr.test(dataframe[42:49])
main_trait_correlations_df = as.data.frame(main_trait_correlations$r) #extracting correlations from the corr.test

kable(main_trait_correlations_df, digits = 4, align = "c", format = "pandoc", caption = "Main Trait Correlations")

```


Stereotypicality scores - two stereotype scores per participant (one male and one female)
```{r}

dataframe$male_stereotype = ((dataframe$competence + dataframe$ambition + dataframe$project + dataframe$independent + dataframe$self_reliant + dataframe$decisive + dataframe$confident + dataframe$dominant + dataframe$forceful + dataframe$analytic + dataframe$logical + dataframe$objective)/12)

dataframe$female_stereotype = ((dataframe$obedient + dataframe$respectful+ dataframe$self_erase + dataframe$warm + dataframe$friendly + dataframe$cooperative + dataframe$sharp + dataframe$intuitive + dataframe$insightful + dataframe$friendly + dataframe$caring + dataframe$considerate)/12)

```


Creating new variable in order to tell experiment 1 and experiment 2 apart 
Experiment 1 including standard male candidate and standard female candidate is called 0
Experiment 2 including competent female candidate and warm female candidate is called 1 
```{r}

dataframe = within(dataframe, {
    experiment = ifelse(cond == "Standard male candidate" | cond == "Standard female candidate", 1, 2)
 })

```


Vote as outcome
```{r}

votemodel1 = lm(vote ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(votemodel1)

votemodel2 = lm(vote ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(votemodel2)

```

Representation (me) within foreign policy as outcome
```{r}

me_foreign1 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_foreign1)

me_foreign2 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_foreign2)

```

Representation (me) within education policy as outcome
```{r}

me_education1 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_education1)

me_education2 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_education2)

```

Representation (me) within health policy as outcome
```{r}

me_health1 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_health1)

me_health2 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_health2)

```

Representation (me) within law policy as outcome
```{r}

me_law1 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_law1)

me_law2 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_law2)

```


Representation (dk) within foreign policy as outcome
```{r}

dk_foreign1 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_foreign1)

dk_foreign2 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_foreign2)

```

Representation (dk) within education policy as outcome
```{r}

dk_education1 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_education1)

dk_education2 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_education2)

```

Representation (dk) within health policy as outcome
```{r}

dk_health1 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_health1)

dk_health2 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_health2)

```

Representation (dk) within law policy as outcome
```{r}

dk_law1 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_law1)

dk_law2 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_law2)

```

Sociability as outcome
```{r}

socmodel1 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(socmodel1)

socmodel2 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(socmodel2)

```

Trustworthiness as outcome
```{r}

trustmodel1 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(trustmodel1)

trustmodel2 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(trustmodel2)

```

Suitability as outcome
```{r}

suitmodel1 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(suitmodel1)

suitmodel2 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(suitmodel2)

```







```{r}

library(ggplot2)

bots = ggplot(compdata, aes(x = v1.c, y = PR)) + geom_smooth() + facet_wrap(reliability~authority)
bots


ggplot(dataframe, aes(female_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


ggplot(dataframe, aes(male_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


```

```{r}



```

Dividing the two experiments into two dataframes
```{r}

m_f = dataframe[!(dataframe$cond == "Competent female candidate"),]
m_f = m_f[!(m_f$cond == "Warm female candidate"),]


c_w = dataframe[!(dataframe$cond == "Standard male candidate"),]
c_w = c_w[!(c_w$cond == "Standard female candidate"),]

```