---
title: "Data cleanup"
author: "Sofia F. M. Schmidt-Kallesøe"
date: "9/10/2018"
output: html_document
---

Josh's cleanup
```{r}

library(foreign) #read.spss function

# read SPSS data file
dat_in = read.spss("/Users/Fred/Documents/Aarhus/5. Semester/Bachelor/Gender in politics data/DK2017_Lea.sav")

#######################################################
####------Parsing SPSS file into responses to each question

#----------Question 1 ---------------------
# judgements of candidate in vignette
# check with Lea to verify titles
cond <- dat_in$basic_design
competence <-as.numeric(substr(dat_in$Q1_1,1,1))
ambition <-as.numeric(substr(dat_in$Q1_2,1,1))
project <-as.numeric(substr(dat_in$Q1_3,1,1))
obedient <-as.numeric(substr(dat_in$Q1_4,1,1))
respectful<-as.numeric(substr(dat_in$Q1_5,1,1))
self_erase<-as.numeric(substr(dat_in$Q1_6,1,1))
independent<-as.numeric(substr(dat_in$Q1_7,1,1))
self_reliant<-as.numeric(substr(dat_in$Q1_8,1,1))
decisive<-as.numeric(substr(dat_in$Q1_9,1,1))
warm<-as.numeric(substr(dat_in$Q1_10,1,1))
friendly<-as.numeric(substr(dat_in$Q1_11,1,1))
cooperative<-as.numeric(substr(dat_in$Q1_12,1,1))
sharp<-as.numeric(substr(dat_in$Q1_13,1,1))
intuitive<-as.numeric(substr(dat_in$Q1_14,1,1))
insightful<-as.numeric(substr(dat_in$Q1_15,1,1))
confident<-as.numeric(substr(dat_in$Q1_16,1,1))
dominant<-as.numeric(substr(dat_in$Q1_17,1,1))
forceful<-as.numeric(substr(dat_in$Q1_18,1,1))
analytic<-as.numeric(substr(dat_in$Q1_19,1,1))
logical<-as.numeric(substr(dat_in$Q1_20,1,1))
objective<-as.numeric(substr(dat_in$Q1_21,1,1))
friendly2<-as.numeric(substr(dat_in$Q1_22,1,1))
caring<-as.numeric(substr(dat_in$Q1_23,1,1))
considerate<-as.numeric(substr(dat_in$Q1_24,1,1))

#------Question 2 and 3 ---------------------------
# representation
foreign_me <- as.numeric(substr(dat_in$Q2_1,1,1))
education_me <- as.numeric(substr(dat_in$Q2_2,1,1))
health_me <- as.numeric(substr(dat_in$Q2_3,1,1))
law_me <- as.numeric(substr(dat_in$Q2_4,1,1))

foreign_dk <- as.numeric(substr(dat_in$Q3_1,1,1))
education_dk <- as.numeric(substr(dat_in$Q3_2,1,1))
health_dk <- as.numeric(substr(dat_in$Q3_3,1,1))
law_dk <- as.numeric(substr(dat_in$Q3_4,1,1))

#------Question 4 ---------------------------
# judgements of sociability and trustworthyness
sociability <- rowSums(cbind(as.numeric(substr(dat_in$Q4a_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4b_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4c_socialibility,1,1)),
                             as.numeric(substr(dat_in$Q4d_socialibility,1,1))))

trustworthy <- rowSums(cbind(as.numeric(substr(dat_in$Q4e_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4f_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4g_moral_trustworthy,1,1)),
                             as.numeric(substr(dat_in$Q4h_moral_trustworthy,1,1))))

#------Question 5, 6, and 7 ---------------------------
# voting, suitability, and ability to explicitly recall target gender
vote <- as.numeric(substr(dat_in$Q5,1,1))
gender_suitability <- as.numeric(substr(dat_in$Q6,1,1))
gender_recall <- dat_in$Q7

gender_correct <- rep(1,length(gender_recall))
gender_correct[cond=="Standard female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Warm female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Competent female candidate"&gender_recall == "Mand"]=0
gender_correct[cond=="Standard male candidate"&gender_recall == "Kvinde"]=0
gender_correct[gender_recall == "Ved ikke"]=0

#------ participant demographics and experiment/condition information
gender <- dat_in$gender

age <- dat_in$profile_age

education <- dat_in$profile_education_rc

experiment <- rep(1,length(competence))
experiment[cond=="Warm female candidate"|cond=="Competent female candidate"] <- 2

sub <- dat_in$RecordNo


```

Creating one big dataframe with all the data
```{r}

participant = list(1:1006) #list of numbers 1-1006

dataframe1 = data.frame(participant, cond, 
                       
                       competence, ambition, project, 
                       independent, self_reliant, decisive, 
                       analytic, logical, objective,
                       confident, dominant, forceful,
                       obedient, respectful, self_erase,  
                       warm, friendly, cooperative, 
                       sharp, intuitive, insightful,  
                       friendly2, caring, considerate, 
                       
                       foreign_me, education_me, health_me, law_me,
                       foreign_dk, education_dk, health_dk, law_dk,
                       
                       sociability, trustworthy,
                       
                       vote, gender_suitability, gender_recall, gender_correct, gender, age, education)

dataframe1 = plyr::rename(dataframe1, c("X1.1006" = "participant")) #renaming participant column

```


Renaming genders from Danish to English 
```{r}

levels(dataframe1$gender)[match("Mand",levels(dataframe1$gender))] <- "Male"
levels(dataframe1$gender)[match("Kvinde",levels(dataframe1$gender))] <- "Female"

```


Removing data from people who didn't recall gender correctly 
```{r}

dataframe = dataframe1[!(dataframe1$gender_correct == "0"),]

```


Adding main traits in the dataframe 
```{r}

dataframe$achievement_orientation = (dataframe$competence + dataframe$ambition + dataframe$project)/3
dataframe$autonomy = (dataframe$independent + dataframe$self_reliant + dataframe$decisive)/3
dataframe$take_charge = (dataframe$confident + dataframe$dominant + dataframe$forceful)/3
dataframe$rational = (dataframe$analytic + dataframe$logical + dataframe$objective)/3
dataframe$affiliative = (dataframe$warm + dataframe$friendly + dataframe$cooperative)/3
dataframe$deference = (dataframe$obedient + dataframe$respectful + dataframe$self_erase)/3
dataframe$emotionally_sensitive = (dataframe$sharp + dataframe$intuitive + dataframe$insightful)/3
dataframe$concern_for_others = (dataframe$friendly2 + dataframe$caring + dataframe$considerate)/3

```


Stereotypicality scores - two stereotype scores per participant (one male and one female)
The scores consist of an average of the agentic and communal traits respectively for each participant 
```{r}

dataframe$male_stereotype = ((dataframe$competence + dataframe$ambition + dataframe$project + dataframe$independent + dataframe$self_reliant + dataframe$decisive + dataframe$confident + dataframe$dominant + dataframe$forceful + dataframe$analytic + dataframe$logical + dataframe$objective)/12)

dataframe$female_stereotype = ((dataframe$obedient + dataframe$respectful+ dataframe$self_erase + dataframe$warm + dataframe$friendly + dataframe$cooperative + dataframe$sharp + dataframe$intuitive + dataframe$insightful + dataframe$friendly + dataframe$caring + dataframe$considerate)/12)

```


Creating new variable in order to tell experiment 1 and experiment 2 apart 
Experiment 1 including standard male candidate and standard female candidate is called 1
Experiment 2 including competent female candidate and warm female candidate is called 2 
```{r}

dataframe = within(dataframe, {
    experiment = ifelse(cond == "Standard male candidate" | cond == "Standard female candidate", 1, 2)
 })

```


Saving the clean dataframe 
```{r}

write.csv(dataframe, file = "cleanData.csv")

```

