---
title: "Data analysis"
author: "Sofia F. M. Schmidt-Kallesøe"
date: "19/11/2018"
output: html_document
---


```{r}

dataframe = read.csv("cleanData.csv")
library(stats)
library(ggplot2)
library(psych)
library(knitr)
library(xtable)

```


Average of main traits separated by condition  
```{r}

round(by(dataframe$achievement_orientation, dataframe$cond, FUN = mean), 2)
round(by(dataframe$autonomy, dataframe$cond, FUN = mean), 2)
round(by(dataframe$take_charge, dataframe$cond, FUN = mean), 2)
round(by(dataframe$rational, dataframe$cond, FUN = mean), 2)

round(by(dataframe$affiliative, dataframe$cond, FUN = mean), 2)
round(by(dataframe$deference, dataframe$cond, FUN = mean), 2)
round(by(dataframe$emotionally_sensitive, dataframe$cond, FUN = mean), 2)
round(by(dataframe$concern_for_others, dataframe$cond, FUN = mean), 2)

by(dataframe$male_stereotype, dataframe$cond, summary)

plot(density(dataframe$male_stereotype))
plot(density(dataframe$female_stereotype))

```

Making dataframe for experiment 1
```{r}

dataframe1 = subset(dataframe, experiment == "1")

```



Checking reliability with Alpha package for each main trait for all data - EXPERIMENT 1
```{r}

achievement_orientation = subset(dataframe1, select = c(competence, ambition, project))
mean(dataframe1$achievement_orientation)
sd(dataframe$achievement_orientation)
alpha(achievement_orientation)

deference = subset(dataframe1, select = c(obedient, respectful, self_erase))

autonomy = subset(dataframe1, select = c(independent, self_reliant, decisive))
alpha(autonomy)

affiliative = subset(dataframe1, select = c(warm, friendly, cooperative))
alpha(affiliative)

emotionally_sensitive = subset(dataframe1, select = c(sharp, intuitive, insightful))
alpha(emotionally_sensitive)

take_charge = subset(dataframe1, select = c(confident, dominant, forceful))
alpha(take_charge)

rational = subset(dataframe1, select = c(analytic, logical, objective))
alpha(rational)

concern_for_others = subset(dataframe1, select = c(friendly2, caring, considerate))
alpha(concern_for_others)


#########
dffemale_stereotype = subset(dataframe1, select = c(cond, affiliative, deference, emotionally_sensitive, concern_for_others))

mean(dataframe1$female_stereotype)
sd(dataframe1$female_stereotype)
alpha(dffemale_stereotype)

dfmale_stereotype = subset(dataframe1, select = c(cond, achievement_orientation, autonomy, take_charge, rational))
mean(dataframe1$male_stereotype)
sd(dataframe1$male_stereotype)
alpha(dfmale_stereotype)


#########

mean(dataframe1$foreign_me)
sd(dataframe1$foreign_me)

mean(dataframe1$education_me)
sd(dataframe1$education_me)

mean(dataframe1$health_me)
sd(dataframe1$health_me)

mean(dataframe1$law_me)
sd(dataframe1$law_me)


mean(dataframe1$foreign_dk)
sd(dataframe1$foreign_dk)

mean(dataframe1$education_dk)
sd(dataframe1$education_dk)

mean(dataframe1$health_dk)
sd(dataframe1$health_dk)

mean(dataframe1$law_dk)
sd(dataframe1$law_dk)


######
sociability = data.frame(participant, cond, experiment, gender_correct, as.numeric(dat_in$Q4a_socialibility), as.numeric(dat_in$Q4b_socialibility), as.numeric(dat_in$Q4c_socialibility), as.numeric(dat_in$Q4d_socialibility))
sociability = sociability[!(sociability$gender_correct == "0"),]
sociability = subset(sociability, experiment == "1")


sociability = subset(sociability, select = c(as.numeric.dat_in.Q4a_socialibility., as.numeric.dat_in.Q4b_socialibility., as.numeric.dat_in.Q4c_socialibility., as.numeric.dat_in.Q4d_socialibility.))
mean(rowMeans(sociability))
sd(rowMeans(sociability))
alpha(sociability)


####
trustworthy = data.frame(participant, cond, experiment, gender_correct, as.numeric(dat_in$Q4e_moral_trustworthy), as.numeric(dat_in$Q4f_moral_trustworthy), as.numeric(dat_in$Q4g_moral_trustworthy), as.numeric(dat_in$Q4h_moral_trustworthy))
trustworthy = trustworthy[!(trustworthy$gender_correct == "0"),]
trustworthy = subset(trustworthy, experiment == "1")


trustworthy = subset(trustworthy, select = c(as.numeric.dat_in.Q4e_moral_trustworthy., as.numeric.dat_in.Q4f_moral_trustworthy., as.numeric.dat_in.Q4g_moral_trustworthy., as.numeric.dat_in.Q4h_moral_trustworthy.))
mean(rowMeans(trustworthy))
sd(rowMeans(trustworthy))
alpha(trustworthy)

####

mean(dataframe1$vote)
sd(dataframe1$vote)

#####

mean(dataframe1$gender_suitability)
sd(dataframe1$gender_suitability)


```

EXPERIMENT 2
```{r}

dataframe2 = subset(dataframe, experiment == "2")

```


Checking reliability with Alpha package for each main trait for all data - EXPERIMENT 2
```{r}

#########
dffemale_stereotype = subset(dataframe2, select = c(affiliative, deference, emotionally_sensitive, concern_for_others))
mean(dataframe2$female_stereotype)
sd(dataframe2$female_stereotype)
alpha(dffemale_stereotype)

dfmale_stereotype = subset(dataframe2, select = c(achievement_orientation, autonomy, take_charge, rational))
mean(dataframe2$male_stereotype)
sd(dataframe2$male_stereotype)
alpha(dfmale_stereotype)

#########

mean(dataframe2$foreign_me)
sd(dataframe2$foreign_me)

mean(dataframe2$education_me)
sd(dataframe2$education_me)

mean(dataframe2$health_me)
sd(dataframe2$health_me)

mean(dataframe2$law_me)
sd(dataframe2$law_me)


mean(dataframe2$foreign_dk)
sd(dataframe2$foreign_dk)

mean(dataframe2$education_dk)
sd(dataframe2$education_dk)

mean(dataframe2$health_dk)
sd(dataframe2$health_dk)

mean(dataframe2$law_dk)
sd(dataframe2$law_dk)


######
sociability = data.frame(participant, cond, experiment, gender_correct, as.numeric(dat_in$Q4a_socialibility), as.numeric(dat_in$Q4b_socialibility), as.numeric(dat_in$Q4c_socialibility), as.numeric(dat_in$Q4d_socialibility))
sociability = sociability[!(sociability$gender_correct == "0"),]
sociability = subset(sociability, experiment == "2" & cond == "Warm female candidate")



sociability2 = subset(sociability, select = c(as.numeric.dat_in.Q4a_socialibility., as.numeric.dat_in.Q4b_socialibility., as.numeric.dat_in.Q4c_socialibility., as.numeric.dat_in.Q4d_socialibility.))
mean(rowMeans(sociability2))
sd(rowMeans(sociability2))
alpha(sociability)


####
trustworthy = data.frame(participant, cond, experiment, gender_correct, as.numeric(dat_in$Q4e_moral_trustworthy), as.numeric(dat_in$Q4f_moral_trustworthy), as.numeric(dat_in$Q4g_moral_trustworthy), as.numeric(dat_in$Q4h_moral_trustworthy))
trustworthy = trustworthy[!(trustworthy$gender_correct == "0"),]
trustworthy = subset(trustworthy, experiment == "2" & cond == "Warm female candidate")


trustworthy = subset(trustworthy, select = c(as.numeric.dat_in.Q4e_moral_trustworthy., as.numeric.dat_in.Q4f_moral_trustworthy., as.numeric.dat_in.Q4g_moral_trustworthy., as.numeric.dat_in.Q4h_moral_trustworthy.))
mean(rowMeans(trustworthy))
sd(rowMeans(trustworthy))
alpha(trustworthy)

####

mean(dataframe2$vote)
sd(dataframe2$vote)

#####

mean(dataframe2$gender_suitability)
sd(dataframe2$gender_suitability)


```


```{r}

plot(density(subset(dataframe, cond == "Standard male candidate")$male_stereotype))

ggplot(dataframe, aes(dataframe$female_stereotype)) +
  geom_histogram(colour = "darkblue", fill = "lightblue", binwidth = 0.3) +
  stat_function(fun = dnorm, args = list(mean = mean(dataframe$female_stereotype, na.rm = TRUE), sd = sd(dataframe$female_stereotype, na.rm = TRUE)), size = 1) +
  facet_wrap(~cond) +
  labs(x = "Perceived communality", y = "Density", title = "Perceived communality split by conditions")

ggplot(dataframe, aes(dataframe$male_stereotype)) +
  geom_histogram(colour = "black", fill = "grey", binwidth = 0.3) +
  facet_wrap(~cond) +
  labs(x = "Perceived agency", y = " ", title = "Perceived agency split by condition")


```




Main trait correlations 
```{r}

main_trait_correlations = psych::corr.test(dataframe1[45:52])
main_trait_correlations_df = as.data.frame(main_trait_correlations$r) #extracting correlations from the corr.test

kable(main_trait_correlations_df, digits = 2, align = "c", format = "pandoc", caption = "Main Trait Correlations")

cor.test(dataframe[42:52])
?cor.test

cor.test(dataframe$male_stereotype, dataframe$female_stereotype)


by(dataframe$vote, dataframe$gender, FUN = mean)

```


-------------------------------------------------------------------------------------------------------------------------------



Vote as outcome
```{r}

votemodel1 = lm(vote ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(votemodel1)

votemodel2 = lm(vote ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(votemodel2)



by(subset(dataframe, gender == "Male")$male_stereotype, subset(dataframe, gender == "Male")$cond, FUN = mean)
by(subset(dataframe, gender == "Female")$male_stereotype, subset(dataframe, gender == "Female")$cond, FUN = mean)
by(subset(dataframe, gender == "Male")$female_stereotype, subset(dataframe, gender == "Male")$cond, FUN = mean)
by(subset(dataframe, gender == "Female")$female_stereotype, subset(dataframe, gender == "Female")$cond, FUN = mean)



by(subset(dataframe, gender == "Male")$vote, subset(dataframe, gender == "Male")$cond, FUN = mean)
by(subset(dataframe, gender == "Female")$female_stereotype, subset(dataframe, gender == "Female")$cond, FUN = mean)

t.test(dataframe$vote ~ dataframe$gender)


```

Plotting significant interaction between genderMale:female_stereotype with vote as outcome in experiment 1
```{r}

 ggplot(subset(dataframe, experiment == "1"), aes(female_stereotype, vote, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Female Stereotype", y = "Vote")

```


Plotting significant interaction between condStandardMale:genderMale:female_stereotype with vote as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(female_stereotype, vote, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~gender) +
  labs(x = "Perceived communality", y = "Likeliness to vote", title = "Interaction between target gender, gender of participant and perceived communality")
  
```



Representation (me)
-------------------------------------------------------------------------------------------------------------------------------
Representation (me) within foreign policy as outcome
```{r}

me_foreign1 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_foreign1)

me_foreign2 = lm(foreign_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_foreign2)

```

Representation (me) within education policy as outcome
```{r}

me_education1 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_education1)

me_education2 = lm(education_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_education2)

```

Representation (me) within health policy as outcome
```{r}

me_health1 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_health1)

me_health2 = lm(health_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_health2)

```

Representation (me) within law policy as outcome
```{r}

me_law1 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(me_law1)

me_law2 = lm(law_me ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(me_law2)

```
-------------------------------------------------------------------------------------------------------------------------------


Representation (dk)
-------------------------------------------------------------------------------------------------------------------------------

Representation (dk) within foreign policy as outcome
```{r}

dk_foreign1 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_foreign1)

dk_foreign2 = lm(foreign_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_foreign2)

```


Plotting significant interaction between genderMale:male_stereotype with foreign_dk as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(male_stereotype, foreign_dk, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Perceived agency", y = "Representation of Denmark within foreign politics", title = "Interaction between participant gender and perceived agency")

#  To which degree does the political candidate represent you within the following areas



?geom_smooth
```

Plotting significant interaction between condStandardMale:genderMale:male_stereotype with foreign_dk as outcome in experiment 1
```{r}

ggplot(subset(dataframe, experiment == "1"), aes(male_stereotype, foreign_dk, colour = gender)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~cond) +
  labs(x = "Perceived agency", y = "Representation of Denmark within foreign politics", title = "Interaction between target gender, participant gender and perceived agency")

```




Representation (dk) within education policy as outcome
```{r}

dk_education1 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_education1)

dk_education2 = lm(education_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_education2)

```


Plotting significant interaction between condWarmFemale:female_stereotype with education_dk as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, education_dk, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  labs(x = "Perceived communality", y = "Representation of Denmark within education policy", title = "Interaction between perceived gender stereotype conformity
       and perceived communality")

```




Representation (dk) within health policy as outcome
```{r}

dk_health1 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_health1)

dk_health2 = lm(health_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_health2)

```

Representation (dk) within law policy as outcome
```{r}

dk_law1 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(dk_law1)

dk_law2 = lm(law_dk ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(dk_law2)

```


Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with law_dk as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, law_dk, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~gender) +
  labs(x = "Perceived communality", y = "Representationof Denmark within law policy", title = "Interaction between perceived gender stereotype conformity, 
       participant gender, and perceived communality")

```


-------------------------------------------------------------------------------------------------------------------------------

Sociability
-------------------------------------------------------------------------------------------------------------------------------

Sociability as outcome
```{r}

socmodel1 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(socmodel1)

socmodel2 = lm(sociability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(socmodel2)

```
-------------------------------------------------------------------------------------------------------------------------------

Trustworthiness
-------------------------------------------------------------------------------------------------------------------------------

Trustworthiness as outcome
```{r}

trustmodel1 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(trustmodel1)

trustmodel2 = lm(trustworthy ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(trustmodel2)

```


Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with trustworthiness as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, trustworthy, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~gender) +
  labs(x = "Perceived communality", y = "Perceived trustworthiness", title = "Interaction between perceived gender stereotype conformity, 
       participant gender, and perceived communality")

```



-------------------------------------------------------------------------------------------------------------------------------

Suitability
-------------------------------------------------------------------------------------------------------------------------------

Suitability as outcome
```{r}

suitmodel1 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 1))
summary(suitmodel1)

suitmodel2 = lm(gender_suitability ~ cond*gender*(male_stereotype + female_stereotype), data = subset(dataframe, experiment == 2))
summary(suitmodel2)

suitmodel3 = lm(gender_suitability ~ (male_stereotype + female_stereotype)cond*gender, data = subset(dataframe, experiment == 2))
summary(suitmodel3)

```

Plotting significant interaction between condWarmFemale:genderMale:female_stereotype with suitability as outcome in experiment 2
```{r}

ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, gender_suitability, colour = cond)) +
  geom_point() +
  geom_smooth(method ="lm", alpha = 0.3) +
  facet_wrap(~gender) +
  labs(x = "Perceived communality", y = "Perceived suitability for political work", title = "Interaction between perceived gender stereotype conformity, 
       participant gender, and perceived communality")

```

-------------------------------------------------------------------------------------------------------------------------------







```{r}

library(ggplot2)


ggplot(dataframe, aes(female_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


ggplot(dataframe, aes(male_stereotype, vote, colour = gender)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(fill = gender), alpha = 0.2) +
  facet_wrap(~cond)


```

PLOTS
```{r}

library(ggplot2)

#Histograms of stereotypes
plot(hist(dataframe$male_stereotype))
plot(hist(dataframe$female_stereotype))



ggplot(dataframe, aes(female_stereotype, vote)) + 
  geom_point() + 
  geom_smooth(method = "lm")

ggplot(dataframe, aes(male_stereotype, vote)) + 
  geom_point() + 
  geom_smooth(method = "lm")

ggplot(dataframe, aes(female_stereotype, vote, colour = gender)) +
  stat_summary(fun.y = mean, geom = "point") + 
  stat_summary(fun.y = mean, geom = "line", aes(group = gender)) + 
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  facet_wrap(~cond)
#remember stereotypes 


plot(dataframe$female_stereotype[dataframe$experiment=="2" & dataframe$gender=="Female" & dataframe$cond=="Warm female candidate"],
     dataframe$suitability[dataframe$experiment=="2" & dataframe$gender=="Female" & dataframe$cond=="Warm female candidate"])


ggplot(subset(dataframe, experiment == "2"), aes(female_stereotype, gender_suitability)) + 
  facet_wrap(cond~gender) +
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Female Stereotype", y = "Gender Suitability")








```



```{r}

count(subset(dataframe1, experiment == "2")$gender == "Female")

plot(subset(dataframe, experiment == "2")$age)


```